%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Product Manager, Microsoft Outlook} % Job title
    {Microsoft} % Organization
    {} %URL
    {Seattle, WA} % Location
    {Sept. 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead product strategy, positioning, and execution for Outlook's MCP-based agent platform while contributing directly in .NET and TypeScript to ship significant features across mail, calendar, people, tasks, and extensible UI.}
        \item {Define shared contracts for tool discovery, authentication, authorization, privacy classification, human approvals, auditability, and telemetry---turning partner-specific needs into reusable platform capabilities.}
        \item {Designed and shipped AI-assisted compliance automation that derives required evidence and artifacts from code, automates previously manual submissions, and saves the engineering team dozens of hours each month.}
        \item {Led creation of AI evaluation tooling for agentic hill-climbing across Outlook scenarios; author and maintain evaluation assertions and repeatable experiment pipelines that quantify improvements to model, prompt, and tool behavior.}
        \item {Partner with security, privacy, compliance, and product teams to establish protocol-conformance, failure-handling, and launch gates that balance agent capability, user trust, reliability, and developer velocity.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Product Manager, Microsoft 365 \& Outlook} % Job title
    {Microsoft} % Organization
    {} %URL
    {Seattle, WA} % Location
    {Jun. 2020 - Sept. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Shipped shared platform components across Outlook, Office, and Teams used by 200M+ monthly active users, aligning complex requirements across extensibility surfaces and more than 70 partner teams.}
        \item {Led cross-functional engineering, design, research, and marketing teams from customer discovery through launch; created a multi-year platform vision endorsed by executives across organizations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Product Manager Intern} % Job title
    {Microsoft} % Organization
    {} %URL
    {Seattle, WA} % Location
    {Summers 2018 \& 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built analytics and cost models with Power BI and Kusto that unlocked new Office service use cases and informed cloud-management product strategy for more than 130M managed devices.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Systems Engineering Intern} % Job title
    {Cisco} % Organization
    {} %URL
    {Toronto \& Ottawa, ON, Canada} % Location
    {Summers 2016 \& 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built Webex Teams chatbots and service integrations in Node.js and maintained enterprise networking, infrastructure, and security demo environments supporting major Canadian government opportunities.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder \& Lead Consultant} % Job title
    {Penguinleaf Technologies} % Organization
    {penguinleaf.com} %URL
    {Toronto, ON, Canada} % Location
    {Jun. 2014 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-founded a managed technology consultancy serving dozens of organizations and thousands of users; owned customer discovery, solution architecture, implementation, and ongoing operations.}
        \item {Migrated customers to cloud-managed identity, networking, device management, and productivity platforms, improving security and reliability while reducing total cost of ownership.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
